%-------------------------
% Resume in Latex
% Author : David Ogunbanjo
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape David Ogunbanjo} \\ \vspace{1pt}
    \small Baltimore, MD $|$ 443-985-8675 $|$ 
    \href{mailto:davidogunbanjo15@gmail.com}{\underline{davidogunbanjo15@gmail.com}} $|$
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/...}} $|$
    \href{https://github.com/...}{\underline{github.com/...}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Loyola University Maryland}{Baltimore, MD}
      {Bachelor of Science in Computer Science}{Anticipated May 2027}
      \resumeItemListStart
        \resumeItem{Honors: Loyola Presidential Scholarship, Delegate Scholarship}
        \resumeItem{Scholar Programs: Hyman Science Scholar Program, Hauber Research Fellowship}
        \resumeItem{Relevant Coursework: Object-Oriented Data Structure Design and Analysis, Operating Systems}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------RESEARCH EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hauber Research Fellow}{Summer 2025}
      {Loyola University Maryland}{Baltimore, MD}
      \resumeItemListStart
        \resumeItem{Developed and optimized CNN models for pothole detection in roadway images.}
        \resumeItem{Collected, labeled, and preprocessed datasets using Python, TensorFlow, and Roboflow.}
        \resumeItem{Evaluated model performance using precision, recall, and F1 score.}
        \resumeItem{Collaborated with faculty mentors to prepare a research paper and presentation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Information Technology Technical Services Assistant}{Summer 2024 -- Present}
      {Loyola University Maryland}{Baltimore, MD}
      \resumeItemListStart
        \resumeItem{Installed and configured operating systems and enterprise software on 90\% of campus devices.}
        \resumeItem{Diagnosed and repaired hardware/software issues, improving uptime and user satisfaction.}
      \resumeItemListEnd

    \resumeSubheading
      {Technical Coordinator}{Summers 2023 -- Spring 2024}
      {Westminster, MD}{}
      \resumeItemListStart
        \resumeItem{Created a Power App to automate temperature tracking, improving efficiency by 40\%.}
        \resumeItem{Streamlined data systems through SharePoint and Excel automation.}
      \resumeItemListEnd

    \resumeSubheading
      {Information Technology Intern}{Summers 2023}
      {Westminster, MD}{}
      \resumeItemListStart
        \resumeItem{Built a data-tracking app using Power Apps and Power Automate.}
        \resumeItem{Designed and launched a SharePoint site for centralized company documentation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------
\section{Leadership Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Robotics Club}{Fall 2024 -- Present}
      {Vice President}{Loyola University Maryland}
      \resumeItemListStart
        \resumeItem{Oversaw project planning and collaboration with STEM organizations.}
      \resumeItemListEnd

    \resumeSubheading
      {Association for Computing Machinery \& Cybersecurity Club}{Fall 2024 -- Present}
      {Co-President}{Loyola University Maryland}
      \resumeItemListStart
        \resumeItem{Organized technical workshops, hackathons, and networking events.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Personal Portfolio Website}{2024}
      {Technologies: React, Material-UI, Netlify}{} 
      \resumeItemListStart
        \resumeItem{Developed a responsive portfolio website to showcase projects and skills.}
        \resumeItem{Implemented interactive UI components using React and Material-UI.}
      \resumeItemListEnd

    \resumeSubheading
      {Pothole Detection System}{2025}
      {Technologies: Python, TensorFlow, Roboflow}{} 
      \resumeItemListStart
        \resumeItem{Created a CNN model to detect potholes in roadway images with 92\% accuracy.}
        \resumeItem{Individually preprocessed and manually labeled a dataset of 5,000 images for training and validation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL (Postgres), JavaScript, HTML/CSS, laTex} \\
     \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
     \textbf{Developer Tools}{: Git, Docker, TravisCI, Google Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib} \\
     \textbf{Certifications}{: CompTIA A+, CPR}
    }}
 \end{itemize}

\end{document}
